\documentclass{article}
\usepackage{ngerman}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}



\begin{document}
\thispagestyle{empty}
\vspace*{-3.5cm}
\begin{center}
\Large{\textbf{WORKING TITLE::KAFFEESATT}}\\
Bastian Luick(1018266), Jan Witzany(1011713),\\ Juti Boottawong(1030476).
\end{center}
\vspace*{-0.5cm}
\section*{Scope and Specifications of the Project}
To provide miscellaneous information about coffee localities through a web application with students, inbound tourists and coffee fanatics in Kiel.
\vspace*{-0.5cm}
\section*{VISION}
Our Vision is that everyone know where they can find their suitable beverage place.
\vspace*{-0.5cm}
\section*{MISSION}
Provide a sophisticated web application for students, inbound tourists or coffee fanatics to discover a place to relax and enjoy their favorite coffee and supply themselves with coffee making utensil.
\vspace*{-0.5cm}
\section*{W*H}
\textbf{Who will be using the system?}\\
Students, coffee fanatics and inbound tourists that are in Kiel.\\
\textbf{When will be the system be used?}\\
Breaks and Lunches.\\
\textbf{Where is the information system used?}\\
Desktop and Mobile at home, at work, on the go, in the city, near sights.\\
\textbf{What is represented in the system?}\\
Available coffee sorts, price-range, picture gallery, ratings from \textit{Google} etc., direct links to places, misc. information about coffee~(fair trade, preparation process, quality criteria, provenance etc..)\\
\textbf{How will the system be used?}\\
Desktop and Mobile via web browser.\\
\textbf{Why is the system used?}\\
To find the place to enjoy coffee or buy coffee accessories.\\
\textbf{What is the policy, intention, goal, and aim of the provider?}\\
To share our love and knowledge of coffee with coffee drinkers, coffee providers and coffee makers in Kiel.
\vspace*{-0.5cm}
\section*{User \& Scenarios Outline} 
\textbf{Students} much free time, high mobility in the area of Kiel (Student Ticket), bicycle routes, price sensitive\\
Student thirst for coffee at the university during lectures.\\\\
\textbf{Inbound Tourist} no knowledge of Kiel, high price tolerance. \\
Tourist is in the middle of the city during a day trip and want to relax with a coffee.\\\\
\textbf{Coffee fanatics} want to know everything about the coffee or the coffee supplements high expectation, high demand of information, \\
At home and want to explore novel coffee localities.\\
\end{document}