\section{Outlook}

\subsection{External API}
To give the user more input of different opinions about a particular shop the web system should include ratings from Google and sites like Trip-Advisor.
For a better orientation for the user google map should be include as well as cookies to locate the user current location.
\subsection{User Interface / User Experience}
\textbf{Next Up}\\
More Feedback for the user by clicking the search button
Add clean user management system.
Add search functionality in events.
Add search functionality in blends.
Complete update shop functionality.
Generate views to ease performance
Make update possible even with the primary keys.
\textbf{General}\\
Differents color Scheming according to seasons.
Own original Icons for features of the shops.
Login and User Management
More Icons to represent different properties.
Mobile and responsive corresponding sites for the general usage.
Mobile and responsive corresponding especially for the input page.
Further enhance all search functionality.
Make rating possible.
More user behaviour(validations) control like opening time not less than closing time etc.
\textbf{Input Content}
Possible to input several contents on one click.
Pop up or another  method so that it is possible to select as well as input content directly in regards to the shop-tab.

\subsection{Behavioral Management}
\textbf{General}\\
Can choose how much information is show on. 
\textbf{Fanatics}\\
Make possible to create List of favourites shops.
Can Adjust amount of checkboxes in the search box.
Make it possible to show selling object of specific shop. 
\textbf{Tourist}\\
