\section{Quantity Analysis}
The given numbers besides the entity- and relationshiptyps is a guess of the data volume which our database will store.
\paragraph{ENTITY}
\begin{itemize}
\item SHOP: 55
\item USER: 300
\item COMPANY: 37
\item COFFEE\_DRINK: 20
\item BLEND: 29
\item BEANS: 29
\item EVENT: 33
\item POI: 28
\end{itemize}



\paragraph{RELATIONSHIP}
A CoffeeShop belongs to excatly \textbf{1} Company. Also it has \textbf{7} OpeningTimes for each day of the week. We assume an average amount of \textbf{3} BusStations and \textbf{2} POIs for each CoffeeShop. It severs about \textbf{30} beverages and offers \textbf{10} Beans, \textbf{20} Blends and \textbf{4} EquipmentCategories. For future profe we provide a sells Table where Shops can offer specific Equipment models, but we do not consider it yet.\\
A CoffeeShop can organizes several Events, we calculate with a average about \textbf{5} Events per year. We do not delete expired Events yet, this might be implemented in later work.
 


\paragraph{CLUSTER}
\begin{itemize}
\item ARTICLE: 0
\item ARTICLE\_BEAN: 0
\item ARTICLE\_DRINK: 0
\item ARTICLE\_BLEND: 0
\end{itemize}

\vspace{8px}

\begin{itemize}
\item GOOGLE-RATING:0
\item TRIPADVISOR-RATING:0
\item USER-RATING:300?
\end{itemize}




\paragraph{Function Calls}
Frequency of usage of functionality differentiated between content-manager and regular user:
\subparagraph{Content-Manger}
\begin{itemize}
\item Create:	300 per year
\item Update: 1000 per year
\item Delete: 50 per year
\end{itemize}

\subparagraph{User}
\begin{itemize}
\item Search: 400 per day
\item Filter:	300 per day
\end{itemize}
